Collaborative Infrastructure for Test-Driven\\Scientific Model Validation

### 2014-03-13 sciunit-icse14/sciunit-icse14.tex
Changes for reviewers

Before explaining the details of this example, we point out that SciUnit is implemented in Python. Python is one of the most widely used languages in science today \cite{sanner1999python}. It supports calling into  many of the other popular languages, including R, MATLAB, C and Java, more cleanly than these languages support calling into Python (challenge 3). It is widely-recognized as being easy-to-read and its object system can be used to define abstract interfaces, which we leverage in support of challenge 2.

@@

While we discuss a toy example based on planetary movement here, we have applied this framework to more realistic problems in neurobiology and have bridged SciUnit to large-scale neuroinformatics projects (we anticipate publishing a description of these case studies shortly). Much future work remains to be done to investigate whether these tools are truly usable and useful to scientific communities, to further develop the community workflow and infrastructure and to develop a range of realistic case studies. Nevertheless, we believe that identifying the synergies between testing practices and model validation, and describing the basic tooling, represents a novel contribution to the literature on software testing. The core SciUnit framework has been fully developed and is available at http://sciunit.scidash.org/. SciDash is under active development, and is currently capable of basic forms of the operations described in Sec. 3. %In particular, we consider modeling competitions in science as a form of test-driven validation. For example, the quantitative single neuron modeling competition (QSNMC) \cite{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes, and 
%examples from other subfields of biology abound (e.g. \url{http://www.the-dream-project.org}).  These competitions typically use \emph{ad hoc} infrastructure. A common framework could be used to make designing and continuously operating such contests more feasible. In related work that

>>>>

Before explaining the details of this example, we point out that SciUnit is implemented in Python. Python is one of the most widely used languages in science today \cite{sanner1999python}, and has become the de facto language of open source scientific computing. It supports calling into  many of the other popular languages, including R, MATLAB, C and Java, more cleanly than these languages support calling into Python (challenge 3). It is widely-recognized as being easy-to-read and its object system can be used to define abstract interfaces, which we leverage in support of challenge 2. Alternative implementations of SciUnit, including language-independent specifications of its structure, may be part of future work.

@@

While we discuss a toy example based on planetary movement here, we have applied this framework to more realistic problems in neurobiology in a project called NeuronUnit (http://github.com/scidash/neuronunit). We have used this as part of a collaboration with a large-scale neuroinformatics project (http://www.opensourcebrain.org), whose developers are enthusiastic about a practical pipeline for testing the dozens of models they currently maintain. Much future work remains to be done to investigate whether these tools are truly usable and useful to scientific communities, to further develop the community workflow and infrastructure and to develop a range of realistic case studies. Nevertheless, we believe that identifying the synergies between testing practices and model validation, and describing the basic tooling, represents a novel contribution to the literature on software testing. The core SciUnit framework has been fully developed and is available at http://sciunit.scidash.org/. SciDash is under active development, and is currently capable of basic forms of the operations described in Sec. 3.

We also plan to use SciUnit to implement competitions among classes of models or techniques in particular subfields. Typically such competitions use \emph{ad hoc} infrastructure. A common framework could be used to make designing and continuously operating such contests more feasible.
